\section{Directors' Report}

\subsection{Objects of the Company}

The stated Objects of the Hackspace Foundation are:

\begin{itemize}
    \item To promote and support science, engineering, and art.
\end{itemize}

The main activity of the company is providing permanent community workspace facilities in the London area (the London Hackspace).
We aim to provide a comfortable place where people can learn new skills, socialise, and gain access to tools they would not otherwise have access to.

\subsection{Organisational Structure}\label{ref_structure}

The Hackspace Foundation is a Company Limited by Guarantee operating as a membership association.
The company has a Board of up to eight Directors who are elected by the membership and serve for a three-year term,
although this is mainly a symbolic role with most decisions made by membership consensus.

As the Foundation has grown since its formation in February 2009, it has historically not been possible
to reliably determine if it is eligible for charitable status. Combined with the administrative overhead of doing so,
this has so far prevented the Hackspace Foundation from becoming a registered charity.

Since the company is becoming more mature, it is becoming more clear that it is likely to be eligible for charitable status,
and we anticipate looking into applying within the next year.

\subsection{Facilities}

At the beginning of the 2010/2011 year, the London Hackspace was based in an 800 sq ft, unheated space in Barnsbury.
In July 2010 we moved to a 1300 sq ft space in Cremer Street, E2, and on January 1\(^{st}\) 2011 the space was expanded into
the adjacent unit to increase our space to 2600 sq ft.

Currently our space comprises desk space across two separate rooms, sofas, a kitchen, and a sizeable workshop with woodworking,
metalworking and other fabrication facilities.

Recent equipment purchases include a laser cutter for cutting and etching wood and plastic, and large lathe/mill for metalworking.
All this equipment is available for members to use for free or with a small contribution to equipment running costs.

\subsection{Membership}

The Hackspace Foundation is a membership association, and membership is open to everyone.
Members receive 24-hour access to the space, storage space, and voting rights in return for a membership subscription.

The minimum membership subscription is £5 per month, and members are encouraged to pay what they consider their
membership to be worth.

Membership subscriptions are the primary source of income for the Hackspace Foundation, and in 2010/11 our
membership rapidly grew by 600\% from 41 to 252 people.

\subsection{Services for Non-Members}

Although we encourage anyone who finds the London Hackspace useful to become a member, we don't limit our services to members.
Non-members can use our facilities under the supervision of a member, and we run events (both free and paid) which are open to non-members.

There are many individual events organised by members on a regular basis, which are usually free and open to the public. Regular events include:

\begin{itemize}
    \item Weekly Meetups - our weekly public social events.
    \item DIY Bio - workshops and lectures on biology.
    \item Young Hackspace - free events for children aged between 6 and 10.
\end{itemize}

We also allow other like-minded non-profit groups to hire out sections of our space at cost - generally much cheaper than other similar venues.

\subsection{Public Benefit}

The London Hackspace is not currently a registered charity (see the Organisational Structure section on page \pageref{ref_structure} for more details),
which would require it to publish details of the public benefit it delivers. Nonetheless, the Directors feel it is appropriate to do so.

We believe the London Hackspace delivers charitable benefits under two of the headings allowed by the Charities Act 2006:
firstly and primarily through the advancement of the arts, culture, heritage or science, and secondly through the advancement of education.

As entry to the London Hackspace is free of charge for non-members, and the minimum membership is a modest fee, we
believe there are no unreasonable restrictions on access to the benefits which are therefore available to the public in accordance with the
definition of the Act.

\subsection{Reserves Policy}

The Hackspace Foundation aims to keep three months worth of monthly running costs as a reserve. This currently amounts to £12,486.

Due to the significant membership growth of the London Hackspace during 2010/11, it was decided to spend some of the reserve on expanding the space.
The majority of this was spent on lease deposits. At the end of the financial year, our balance was £7,568.

\subsection{Statement of Directors' Responsibilities}
The directors are responsible for preparing the Directors' Report and the financial statements in accordance with applicable law and regulations.

Company law requires the directors to prepare financial statements for each financial year. Under that law the directors have elected to prepare the financial statements in accordance with United Kingdom Generally Accepted Accounting Practice (United Kingdom Standards and applicable law). Under company law the directors must not approve the financial statements unless they are satisfied that they give a true and fair view of the state of affairs of the company and of the profit or loss of the company for that period. In preparing these financial statements, the directors are required to:

\begin{itemize}
    \item select suitable accounting policies and then apply them consistently;
    \item make judgements and accounting estimates that are reasonable and prudent;
    \item prepare the financial statements on the going concern basis unless it is inappropriate to presume that the company will continue in business.
\end{itemize}

The directors are responsible for keeping adequate accounting records that are sufficient to show and explain the company's transactions and disclose with reasonable accuracy at any time the financial position of the company and enable them to ensure that the financial statements comply with the Companies Act 2006. They are also responsible for safeguarding the assets of the company and hence for taking reasonable steps for the prevention and detection of fraud and other irregularities.

This report has been prepared in accordance with the special provisions relating to small companies within Part 15 of the Companies Act 2006.

Approved by the Board for issue on <date>
\vspace{48pt}

Russell Garrett \\
{\bf Director} \\
Company Number: 06807563
