\section{Directors' Report}

\subsection{Objects of the Association}

The stated Objects of London Hackspace are:

\begin{itemize}
    \item to promote and encourage technical, scientific, and artistic skills through social collaboration and education; and
    \item to provide and maintain shared community workspace and equipment in Greater London.
\end{itemize}

The main activity of the company is providing permanent community workspace facilities in the London area (the London Hackspace).
We aim to provide a comfortable place where people can learn new skills, socialise, and gain access to tools they would not otherwise have access to.

\subsection{Organisational Structure}\label{ref_structure}

The London Hackspace is a Company Limited by Guarantee operating as a membership association.
The company has a Board of up to nine Directors (known commonly as "Trustees") who are elected yearly by the membership and serve for a three-year term.
The role of the Trustees is primarily to provide overall guidance; day-to-day management of the facilities is handled by members on a volunteer basis.

\subsection{Charitable Status}

In our previous Annual Report, we raised the possibility of applying for charitable status.
After discussion with the Charity Commission during 2011, we concluded that this would not be
an appropriate route for London Hackspace to go down at this time.

\subsection{Facilities}

TBC

\subsection{Membership}

TBC

\subsection{Reserves Policy}

London Hackspace aims to keep three months worth of monthly running costs as a reserve.

\subsection{Statement of Directors' Responsibilities}
The directors are responsible for preparing the Directors' Report and the financial statements in accordance with applicable law and regulations.

Company law requires the directors to prepare financial statements for each financial year. Under that law the directors have elected to prepare the financial statements in accordance with United Kingdom Generally Accepted Accounting Practice (United Kingdom Standards and applicable law). Under company law the directors must not approve the financial statements unless they are satisfied that they give a true and fair view of the state of affairs of the company and of the profit or loss of the company for that period. In preparing these financial statements, the directors are required to:

\begin{itemize}
    \item select suitable accounting policies and then apply them consistently;
    \item make judgements and accounting estimates that are reasonable and prudent;
    \item prepare the financial statements on the going concern basis unless it is inappropriate to presume that the company will continue in business.
\end{itemize}

The directors are responsible for keeping adequate accounting records that are sufficient to show and explain the company's transactions and disclose with reasonable accuracy at any time the financial position of the company and enable them to ensure that the financial statements comply with the Companies Act 2006. They are also responsible for safeguarding the assets of the company and hence for taking reasonable steps for the prevention and detection of fraud and other irregularities.

This report has been prepared in accordance with the special provisions relating to small companies within Part 15 of the Companies Act 2006.

Approved by the Board for issue on TBC
\vspace{48pt}

Russell Garrett \\
{\bf Director} \\
Company Number: 06807563
